Continuous time

### 2023-09-25 analyze.qmd
move file

library(scales)
library(cmdstanr)
library(posterior)
library(brms)
library(ggstance)
library(ggdist)
library(patchwork)
library(tidyverse)
source("functions.R")
```

>>>>

library(scales)
library(cmdstanr)
library(posterior)
library(brms)
library(ggstance)
library(ggdist)
library(patchwork)
library(tidyverse)
source("R/functions.R")
```

### 2023-09-25 continuous-time.qmd
move file

library(scales)
library(cmdstanr)
library(posterior)
library(brms)
library(patchwork)
library(tidyverse)
library(splines)
library(emmeans)
library(lme4)
library(broom.mixed)
library(knitr)
source("functions.R")
source("R/fit_cached.R")
```

>>>>

library(scales)
library(cmdstanr)
library(posterior)
library(brms)
library(patchwork)
library(tidyverse)
library(splines)
library(emmeans)
library(lme4)
library(broom.mixed)
library(knitr)
source("R/functions.R")
source("R/fit_cached.R")
```
